---
title: Who use R
author: ''
date: '2019-01-06'
slug: who-use-r
categories: []
tags: [R]
description: 'who use R'
topics: []
---
## Purpose

Using R download volume to estimate how many people are using R in the world.

There are two data sources:

1. JSON API data from https://cranlogs.r-pkg.org/ 

2. data from package cranlogs which wrap data from https://cranlogs.r-pkg.org/ 
3. CSV data from http://cran-logs.rstudio.com/



## R base download volume by year
There is a tremendous growth in 2018Q4, reaching 140K monthly download at Oct nearly double year of year. 
The growth may due to more school using R at the new semester

```{r echo=FALSE,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(lubridate)
library(jsonlite)

# Make start_day and end_day of each month 
start_day=seq(as.Date("2016-01-01"), as.Date("2018-12-31"), by="month") 
day_df=as.data.frame(start_day)
day_df=day_df%>%mutate(end_day=floor_date(as.Date(start_day), "month")+ months(1)-1)

# download each month total download amount
all_day_df=c()
for (row in 1:nrow(day_df)){
  start_day <- day_df[row, "start_day"]
  end_day  <- day_df[row, "end_day"]
  url=paste0('https://cranlogs.r-pkg.org/downloads/total/',start_day,':',end_day,'/R')
  data <- fromJSON(url)
  all_day_df=rbind(all_day_df,data)
} 

# summary the data
all_day_df=all_day_df%>%mutate(year=year(start),month=month(start),day=day(start))
all_day_df=all_day_df%>%group_by(year,month)%>%summarise(downloads=sum(downloads))

# plot data 
p=plot_ly(data=all_day_df,y=~downloads,x=~month
          ,color = ~as.factor(year)
          ,type = 'scatter', mode = 'lines+markers')
p%>%layout(title = 'R software download')
```
code:http://rpubs.com/estimate/whousingR


## Top 10 R pakcage download at past week
Top R pakcage weekly download around 100K

```{r ,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(plotly)
library(lubridate)

cran_top_downloads("last-week")

```

## package ggplot2 download volume by year

ggplot2 package increase in 2018Q4, reaching 800K monthly download at Oct nearly double year of year. 

```{r ,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(plotly)
library(lubridate)
# downlaod data
R_download=cran_downloads( packages='ggplot2',from='2016-01-01',to='2018-12-31')

# data summary
R_download002=R_download%>%mutate(year=year(date),month=month(date),day=day(date))%>%
  group_by(year,month)%>%summarise(downloads=sum(count))

# plot
p=plot_ly(data=R_download002,y=~downloads,x=~month
          ,color = ~as.factor(year)
          ,type = 'scatter', mode = 'lines+markers')
p%>%layout(title = 'ggplot2 download')

```



## 2018 R base download volume by version






