---
title: Who use R
author: ''
date: '2019-01-06'
slug: who-use-r
categories: []
tags: [R]
description: 'who use R'
topics: []
---
## Purpose
Using R and R package download volume to estimate how many people are using R in the world.

There are two data sources:

1. JSON API data from https://cranlogs.r-pkg.org/ 

2. data from package cranlogs which wrap data from https://cranlogs.r-pkg.org/ 

3. CSV data from http://cran-logs.rstudio.com/

## Conclusion

Estimate total 1-2 milion R user around the world 35% from US and 5% from China with 20% YOY grow.
-------------------------------------------------------------------------------

## R base download volume by year
There is a tremendous growth in 2018Q4, reaching 140K monthly download at Oct nearly double year over year. 
The growth may due to more school using R at the new semester and new R version 3.5 update.

```{r echo=FALSE,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(lubridate)
library(jsonlite)
# Make start_day and end_day of each month 
start_day=seq(as.Date("2016-01-01"), as.Date("2018-12-31"), by="month") 
day_df=as.data.frame(start_day)
day_df=day_df%>%mutate(end_day=floor_date(as.Date(start_day), "month")+ months(1)-1)
# download each month total download amount
all_day_df=c()
for (row in 1:nrow(day_df)){
  start_day <- day_df[row, "start_day"]
  end_day  <- day_df[row, "end_day"]
  url=paste0('https://cranlogs.r-pkg.org/downloads/total/',start_day,':',end_day,'/R')
  data <- fromJSON(url)
  all_day_df=rbind(all_day_df,data)
} 
# summary the data
all_day_df=all_day_df%>%mutate(year=year(start),month=month(start),day=day(start))
all_day_df=all_day_df%>%group_by(year,month)%>%summarise(downloads=sum(downloads))
# plot data 
p=plot_ly(data=all_day_df,y=~downloads,x=~month
          ,color = ~as.factor(year)
          ,type = 'scatter', mode = 'lines+markers',line = list( width = 4))
p%>%layout(title = 'R software download')
```
code:http://rpubs.com/estimate/whousingR


-------------------------------------------------------------------------------

## 2018 R base download volume by version

version 3.5.1 have the most  monthly download

```{r,warning=FALSE ,message=FALSE}
library(tidyverse)
library(plotly)
library(lubridate)
# load data 
version002=read.csv('version002.csv')
p=plot_ly(data=version002,y=~downloads,x=~month    
          ,color = ~version
          ,type = 'scatter', mode = 'lines+markers')
p%>%layout(title = '2018 R base download volume by version')
```


-------------------------------------------------------------------------------

## 2018 R base total download volume by Top 10 country 

2018 Total R base download around 1 Million .US have the most download  378K.China have 50K 
Total R base download around 800K at 2017.

```{r,warning=FALSE ,message=FALSE}
# load data 
library(tidyverse)
library(plotly)
country003=read.csv('country003.csv')
country003%>%filter(year==2018)%>%summarise(downloads=sum(downloads))
country003%>%filter(year==2017)%>%summarise(downloads=sum(downloads))
```


```{r,warning=FALSE ,message=FALSE}
# load data 
library(tidyverse)
library(plotly)
country003=read.csv('country003.csv')
country004=country003%>%group_by(Country)%>%summarise(downloads=sum(downloads))%>%
  top_n(10, wt = downloads)

p=country003%>%filter(Country %in% country004$Country,year==2018)%>%
  plot_ly(x = ~downloads, y = ~fct_reorder(Country, downloads)) %>%
  add_markers() %>%
  layout(xaxis = list(title = "downloads"),
         yaxis = list(title = "Country", type = "category"))

p%>%layout(title = '2018 R base total download volume by Top 10 country')
```
-------------------------------------------------------------------------------

## Top 10 R pakcage download at past week
Top R pakcage weekly download around 100K

```{r ,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(plotly)
library(lubridate)
cran_top_downloads("last-week")
```

-------------------------------------------------------------------------------

## package ggplot2 download volume by year

ggplot2 package increase in 2018Q4, reaching 800K monthly download at Oct nearly double year over year. 

```{r ,warning=FALSE ,message=FALSE}
library(cranlogs)
library(dplyr)
library(plotly)
library(lubridate)
# downlaod data
R_download=cran_downloads( packages='ggplot2',from='2016-01-01',to='2018-12-31')
# data summary
R_download002=R_download%>%mutate(year=year(date),month=month(date),day=day(date))%>%
  group_by(year,month)%>%summarise(downloads=sum(count))
# plot
p=plot_ly(data=R_download002,y=~downloads,x=~month
          ,color = ~as.factor(year)
          ,type = 'scatter', mode = 'lines+markers',line = list( width = 4))
p%>%layout(title = 'ggplot2 download')
```


## Reference
https://www.quora.com/How-many-people-use-R
